\TITLE

### 2024-08-09 paper/main.tex
add Provable Results Availability

The choice between permissioned and permissionless blockchain touches on an ideological dispute about freedom and trust. The use of permissioned blockchain is recommended in domain-specific applications, such as closed consortia between distrustful parties. All the referenced protocols we've found use a public blockchain, suggesting that the fair exchange problem is allegedly not one of them. The public blockchain offers the irreplaceable qualities of total decentralisation, transparency, openness, no infrastructure maintenance costs (only transaction costs) and a different but arguably higher level of security (for networks with a high number of validators). In addition, protocols designed for public blockchains have a higher degree of generality and can be implemented in any private or permissioned blockchain. Therefore, for the rest of the paper, we only consider public networks.

@@

\begin{sloppypar}
A common solution is to use a content addressable peer-to-peer storage network for data storage, as direct blockchain storage is prohibitively expensive. This approach has been widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}. Specifically, data is stored on a network such as IPFS~\cite{benetIPFSContentAddressed2014}, and only the content identifier ($\mathrm{cid}$) that uniquely points to the content on IPFS is published on the blockchain.
\end{sloppypar}

Following this methodology, the SP encrypts the result using the encryption key provided by the client and uploads it to the IPFS network. To ensure the availability of the results, even in cases where the SP is unwilling to share them, we integrate Filecoin as described in Section~\ref{sec:provable-results-availability}.

@@

@@

\noindent \textbf{Package}\label{package} is a physical container prepared by the customer containing all the $\mathrm{materials}$ required by the SP to provide the service.
\[\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})\]
where:
\begin{itemize}
\item $\mathrm{materials}$ - Materials required for the service provision, such as biological samples, legal documents or other relevant items.
\item $\mathrm{provisionID}$ - A unique identifier generated by the customer to anonymously track the provision through all protocol steps.
\item $\mathrm{pk_C}$ - The customer's public key for encrypting results to be published to the public storage network.
\end{itemize}

@@

It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
\begin{eqnarray*}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
\mathrm{sig}_\mathrm{SP}, \\\\ 
\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
\end{eqnarray*}
where:
\begin{itemize}
\item $\mathrm{pk_C}$ - Customer's public key.
\item $\mathrm{provisionID}$ - Unique transaction identifier.
\item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
\item $\mathrm{T}_\mathrm{issue}$ - Time of $\mathrm{PoD}$ issuance.
\item $\mathrm{T}_\mathrm{pay}$ - Payment deadline.
\item $\mathrm{T}_\mathrm{provide}$ - Service provision deadline.
\end{itemize}

@@

The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
\begin{eqnarray*}
\mathrm{PoP} & \equiv & (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
\end{eqnarray*}

@@

\begin{definition}[Fairness] \label{def:fairness}
Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and 
\[
M_{\sigma_\mathrm{s,p,a}} = 
\begin{cases} 
\{ \mathrm{\sigma_{s+1,p,\normal}}, \mathrm{\sigma_{s+1,p,\abnormal}}, \mathrm{\sigma_{s,p,\dispute}}, \mathrm{\sigma_{s,p,\abdispute}} \} & \text{if } s < 9, a = \normal{} \\
\{ \mathrm{\sigma_{s,p,a}} \} & \text{otherwise} 
\end{cases}
\]
represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$. The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination positions.

@@

>>>>

\begin{sloppypar}
The choice between permissioned and permissionless blockchain touches on an ideological dispute about freedom and trust. The use of permissioned blockchain is recommended in domain-specific applications, such as closed consortia between distrustful parties. All the referenced protocols we've found use a public blockchain, suggesting that the fair exchange problem is allegedly not one of them. The public blockchain offers the irreplaceable qualities of total decentralisation, transparency, openness, no infrastructure maintenance costs (only transaction costs) and a different but arguably higher level of security (for networks with a high number of validators). In addition, protocols designed for public blockchains have a higher degree of generality and can be implemented in any private or permissioned blockchain. Therefore, for the rest of the paper, we only consider public networks.
\end{sloppypar}

@@

Even though the result does not contain private information (because the input data did not have it) we acknowledge the danger of storing on a distributed immutable record as blockchain.

\begin{sloppypar}
A common solution is to use a content addressable peer-to-peer storage network for data storage. This approach has been widely adopted in various applications~\cite{shahidBlockchainBasedAgriFoodSupply2020, wangAuditableProtocolsFair2019, chenImprovedP2PFile2017}. Specifically, data is stored on a network such as IPFS~\cite{benetIPFSContentAddressed2014}, and only the content identifier ($\mathrm{cid}$) that uniquely points to the content on IPFS is published on the blockchain.
\end{sloppypar}

Following this methodology, the SP encrypts the result using the encryption key provided by the client and uploads it to the IPFS network.

The result is stored on public network so it is accessible to anyone with the cid address. However, the result is encrypted, so even if downloaded by third party it doesn't get access to the file unless it obtains the client's or SP's private key.

@@

\subsection{Provable Results Availability}

The demand-driven and opportunistic nature of IPFS storage means that the results may not be available indefinitely.

To ensure the availability of the results, we see two approaches. One involves fraud proofs, where an user which can not access the results invoke oracle service like Chainlink Request~\cite{breidenbachChainlinkNextSteps2021, ChainlinkMakeGET} which proves the content unavailability, and so pentalise the SP.

The other approach is to integrate Filecoin as a decentralised pinning service to ensure the results are available for a defined period.

Filecoin enhances content availability on the IPFS network by economically penalizing the lack of proof of content storage~\cite{filecoinSlashing}.

The content availability is therefore economically guaranteed for the duration of the Filecoin contract.

Then, a file that is not further paid for in the Filecoin network is naturally deleted from the network as there is not incentive to keep it.

In this paper we explore the second approach and leave the first for future work.

@@

\noindent \textbf{Package}\label{package} is a physical container prepared by the customer containing all the $\mathrm{materials}$ required by the SP to provide the service.
\begin{equation}
\mathrm{pkg} \equiv (\mathrm{materials}, \mathrm{provisionID}, \mathrm{pk_C})
\end{equation}
where:
\begin{itemize}
\item $\mathrm{materials}$ - Materials required for the service provision, such as biological samples, legal documents or other relevant items.
\item $\mathrm{provisionID}$ - A unique identifier generated by the customer to anonymously track the provision through all protocol steps.
\item $\mathrm{pk_C}$ - The customer's public key for encrypting results to be published to the public storage network.
\end{itemize}

@@

It is also an agreement between the customer and the SP as it contains agreed deadlines for actions and a payment method.
\begin{eqnarray}
\mathrm{PoD} & \equiv & (\begin{array}[t]{l}\mathrm{pk_C}, \mathrm{provisionID},   \mathrm{paymentAddress},
\mathrm{sig}_\mathrm{SP}, \\\\ 
\mathrm{T}_\mathrm{issue}, \mathrm{T}_\mathrm{pay}, \mathrm{T}_\mathrm{provide}\; )\end{array}
\end{eqnarray}
where:
\begin{itemize}
\item $\mathrm{pk_C}$ - Customer's public key.
\item $\mathrm{provisionID}$ - Unique transaction identifier.
\item $\mathrm{paymentAddress}$ - SP's anonymous payment address.
\item $\mathrm{sig}_\mathrm{SP}$ - SP's digital signature.
\item $\mathrm{T}_\mathrm{issue}$ - Time of $\mathrm{PoD}$ issuance.
\item $\mathrm{T}_\mathrm{pay}$ - Payment deadline.
\item $\mathrm{T}_\mathrm{provide}$ - Service provision deadline.
\end{itemize}

@@

The link between $\mathrm{PoP}$ and the results is made by the content identifier ($\mathrm{cid}$), which uniquely identifies the results so that the result cannot be forged after the $\mathrm{PoP}$ has been published.
\begin{equation}
\mathrm{PoP} \equiv (\mathrm{cid}, \mathrm{provisionID}, \mathrm{sig}_\mathrm{SP})
\end{equation}

@@

\begin{definition}[Fairness] \label{def:fairness}
Let $\mathrm{parties} = \{ C, SP \}$, $\mathrm{steps} = 1..9$, $\mathrm{actions} = \{ \normal{}, \abnormal{}, \dispute{}, \abdispute{} \}$, and

\begin{equation}
M_{\sigma_\mathrm{s,p,a}} = 
\begin{cases} 
\{ \mathrm{\sigma_{s+1,p,\normal}}, \mathrm{\sigma_{s+1,p,\abnormal}}, \mathrm{\sigma_{s,p,\dispute}}, \mathrm{\sigma_{s,p,\abdispute}} \} & \text{if } s < 9, a = \normal{} \\
\{ \mathrm{\sigma_{s,p,a}} \} & \text{otherwise} 
\end{cases}
\end{equation}
represent the set of all possible positions a party $\mathrm{p}$ can move to at step $\mathrm{s}$ by taking action $\mathrm{a}$, from position $\sigma_\mathrm{s,p,a}$. The second case in $M_{\sigma_\mathrm{s,p,a}}$ represents the termination positions.

@@

\subsection{Ethical and Regulatory Considerations}

The core objective of our protocol is to facilitate anonymous access to services without necessitating the disclosure of personal information, which naturally raises concerns regarding regulatory compliance, particularly with Know Your Customer (KYC), Anti-Money Laundering (AML), and regulations concerning Politically Exposed Persons (PEP).

Our approach is explicitly designed to integrate with services that inherently comply with applicable local and international regulations. This integration ensures that while our protocol itself operates under the premise of anonymity, it does not facilitate illegal activities or contravene established legal frameworks. Specifically, the services that would utilize our protocol are those not primarily involved in financial transactions or money transmission, thereby not falling directly under the stringent requirements of financial regulations such as KYC and AML.

We acknowledge that the use of anonymous payment methods, such as cryptocurrencies like Monero, might raise suspicions due to their common association with privacy and potential misuse. However, it is important to note that Monero is just one of several anonymous payment methods that could be utilized with our protocol. Our design is versatile enough to support a variety of payment mechanisms, both blockchain-based and non-blockchain-based.

\begin{sloppypar}
For instance, we could employ the Ethereum network and utilize privacy mixers to ensure private payments. Nevertheless, privacy mixers have drawn scrutiny from regulators because they are increasingly used by malicious actors to obscure the origins of funds illicitly. A notable example is Tornado Cash, the largest privacy mixer to date, which has faced sanctions across significant portions of the Ethereum network. Ongoing research into compliant privacy mixers, such as the Voluntary Reveal Approach proposed in~\cite{dotanHazeCompliantPrivacy2023}, seeks to address these concerns. This approach involves Proofs of Innocence required before a user can access the system and incorporates oracles for monitoring sanctioned addresses—currently maintained on the Ethereum blockchain by Chainalysis~\cite{ChainalysisOracleSanctions}.
\end{sloppypar}
